Hazardous asteroids forecast via Markov random fields

### 2021-12-12 Presentation/Presentation.tex
PUB

\begin{center}
Lets Consider the interaction between a planet of mass $m_{1}$ at the  position $r_{1}$ (inertial frame) and an asteroid of mass $m_{2}$  at the position $r_{2}$
\end{center}

\begin{equation}
\textbf{F}_{1}=\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{1}\quad \textbf{F}_{2}=-\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{2}
\end{equation}

If we consider the motion of the second item with respect to the first one

@@

@@

\begin{equation}
\left(\frac{a}{a'}\right)^{3}\approx \left(\frac{T}{T'}'\right)^{2}
\end{equation}

And therefore

\begin{equation}
T'\approx a'^{3/2}
\end{equation}

\begin{center}
\textbf{Remark:} The mass of the asteroid is \textbf{not} involved
\end{center}

>>>>

\begin{center}
The interaction between a planet of mass $m_{1}$ at the  position $r_{1}$ (inertial frame) and an asteroid of mass $m_{2}$  at the position $r_{2}$ is given by: 
\end{center}

\begin{equation}
\textbf{F}_{1}=\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{1} \ddot{\textbf{r}}_{1}\quad \textbf{F}_{2}=-\mathcal{G} \cdot \frac{m_{1}m_{2}}{r^{3}}\textbf{r}=m_{2} \ddot{\textbf{r}}_{2}
\end{equation}

\begin{center}
Where $\mathcal{G}$ is the universal gravitational constant. If we consider the motion of the second item with respect to the first one 
\end{center}

@@

\begin{center}
Consider two asteroids of mass $m$ and $m'$ orbiting the Earth $m_{c}$ , with semi-major axes $a$ and $a'$ and orbital periods $T$ and $T'$
\end{center}

@@

\begin{equation}
\left(\frac{a}{a'}\right)^{3}\approx \left(\frac{T}{T'}\right)^{2}
\end{equation}

\begin{center}
\textbf{Remark:} The mass of the asteroids is \textbf{not} involved
\end{center}
